\iconSection{Experience}{\faChartLine}

\position{Lead Software Developer}{August 2021 - October 2023}{Nuvation Energy}{Waterloo, ON}
\lineSummary{Developing firmware for a scalable Battery Management System (BMS) in Modern C++ and Python.}
\listBegin
\listItem{Owned delivery of full software suite, from start to finish, for one MCU (STM32G0) in BMS. Operated in technical lead capacity, architecting solutions, planning tasks, managing team and reporting to stakeholders. Onboard, mentor, evaluate and report feedback on new hires.}
\listItem{Drove design, implementation, testing, refinement and documentation of firmware for this MCU, including its architecture, drivers, application FSMs, communication protocol and interface. Also led whole development of central MCU's (S7G2) software stackup (driver, API, thread) to manage STM32.}
\listItem{Planned, built, managed and documented tests and custom hardware for continuous validation at all levels (unit, integration, end-to-end) and for different purposes (accuracy, safety, stress). Regularly resolved bugs, regressions and instabilities in performance caught by tests.}
\listItem{Executed systematic and rigorous functional safety analysis on entire software suite. Identified potential failure modes, and developed mitigation techniques and tests. Presented analysis to UL auditor and provided tools to facilitate their external validation.}
\listItem{Designed, developed and documented manufacturing tests, test systems and other test infrastructure.}
\listItem{Gained expertise on main sensor (INA239) controlled by STM32. Was go-to point of contact for team on issues of speed, accuracy, stability, configuration and general use of this part.}
\listEnd

\roleMulti{Hardware \& Software Designer}{June 2020 - August 2021}
% \lineSummary{Developing firmware for a scalable Battery Management System (BMS) in Modern C++ and Python.}
\listBegin
\listItem{Reviewed functional safety analysis of central MCU (S7G2) software. Implemented mitigations and tests.}
\listItem{Ported drivers and threads for central MCU change (TM4C to S7G2) mid-project. Built test system to evaluate new target.}
\listItem{Managed quality of systems, workflows and documentation used by team for development and testing.}
\listItem{Facilitated collaboration between Hardware and Software teams, given holistic background. Provided support from one team to other in design reviews, investigations, product testing.}
\listItem{Wrote customer-facing product documentation in AsciiDoc. Supported customers with technical inquiries about BMS usage.}
\listEnd
% \lineSummary{(External, consulting project) Developing firmware for fiber optic cable-testing instrument in C.}
% \listBegin
% \listItem{Delivered photodiode-measurement software, on an STM32L4, reading trans-impedance amplifier (ADL5304) with an external ADC (AD7176). Wrote complete feature: SPI driver, ADC API, supervising thread (FreeRTOS), external communication API and tests.}
% \listEnd

\roleMulti{Hardware Designer}{September 2018 - June 2020}
\lineSummary{Designing mechanical and electrical components of a BMS and its integrated system in SolidWorks.}
\listBegin
\listItem{Developed multi-stack battery systems' mechanical layout, electrical architecture and stack topology.}
\listItem{Created models, assemblies and drawings for BMS internals, busbars, cables, enclosures and mounting.}
\listItem{Designed for electrical safety to UL standards, and planned high-voltage lab setup for testing.}
\listEnd

% \iconSection{Internships}{\faChartLine}

\roleMulti{Hardware Engineering Co-op}{Summer 2017}
\lineSummary{Fulfilling Integrated Design-to-Manufacturing (IDM) needs for released products.}
% \listBegin
% \listItem{Executed Altium layout updates, team design reviews and fabbed board inspections.}
% \listItem{Investigated isoSPI bug by sniffing traffic with oscilloscope and consulting IC datasheet.}
% \listItem{Reworked boards extensively, being trained to even solder small 0402 SMT packages.}
% \listItem{Designed and built hipot test fixtures that comply with national safety regulations.}
% \listItem{Served in various other IDM-related avenues as needed, such as: building assemblies and cables, creating wiring diagrams in Visio, running in-house production tests, documenting developments in detail, facilitating environmental certification process.}
% \listEnd

\position{Mechatronics Engineering Co-op}{Fall 2016}{KitchenMate Inc.}{Toronto, ON}
\lineSummary{Building electrical and software sub-systems in automated home-cooker.}
% \listBegin
% \listItem{Designed custom linear encoder sensor with photo-interrupter pair and Python driver.}
% \listItem{Sensed heat modes on cooker with hack involving opto-isolator and ADC combination.}
% \listItem{Received abundant exposure and insight on the business side of startup operations.}
% \listItem{Used datasheets to source parts and lab bench-top equipment to test circuit.}
% \listEnd

\position{AI \& Robotics Engineering Co-op}{Winter 2016}{Kindred Systems Inc.}{Toronto, ON}
\lineSummary{Robot-wrangling with Python over distributed communication architecture system.}
% \listBegin
% \listItem{Soldered robots' power boards and executed safety bringup.}
% \listItem{Sourced and integrated components into system with custom-coded drivers.}
% \listItem{Coded behaviour patterns of robots using Finite State Machines (FSMs) in Python.}
% \listItem{Informal intro to ML / N-nets, FK / IK, Grasping, FSM, DB (ES)}
% \listItem{People skills: pair-programming, 1-on-1, standups, blog posts, Happy Hour, AI planning, CI for internal processes, HW concept review}
% \listItem{Python fu: rapid prototyping / scripting AND enterprise-level code i.e. classes, exception-handling, logging, PDB debugging, linting, documentation}
% \listEnd

\position{EDA \& CAD Engineering Co-op}{Summer 2015}{Upverter Inc.}{Toronto, ON}
\lineSummary{Creating 150+ components' symbols and footprints; enhancing CAD features using JavaScript.}
% \lineSummary{Enhancing PCB CAD features in hardware and software avenues.}
% \lineSummary{Creating and verifying symbols and footprints for 150+ electronic components.}
% \listBegin
% \listItem{Created and verified symbols and footprints for 150+ electronic components.}
% \listItem{Used JavaScript to re-factor features and fire-fight bugs extensively.}
% \listItem{Implemented component-tagging feature, using pin names to categorize functionality.}
% \listItem{Adjusted prioritization of design rules in layout constraint manager.}
% \listItem{Fixed incorrect drawing and positioning of constraint violation layout bodies.}
% \listItem{Re-factored click event-listening logic for drawing nets in schematic editor.}
% \listItem{Corrected pin manager's oversight in tracking connection mappings.}
% \listItem{Enabled efficient BGA row enumeration during footprint generation.} % omitting specific letters during row enumeration
% \listEnd

\position{Mechanical Engineering Co-op}{Fall 2014}{Prodomax Automation Inc.}{Barrie, ON}
\lineSummary{Designing custom tooling in automotive assembly line stations for vehicle's seat track, using Solidworks.}
% \lineSummary{Modelling custom jigs and fixtures for automotive part-assembly stations, using Solidworks.}
% \listBegin
% \listItem{Designed two stations in assembly line for vehicle's seat track mechanism.} % Inserted anti-collapse spacer, stamp-pressed bushing.
% \listItem{Detailed and ballooned part and assembly drawings for tooling fabrication.}
% \listItem{Worked around design constraints using critical thinking and teamwork.}
% \listEnd

\position{Neuro-Robotics Lab Research Assistant}{Winter 2014}{University of Waterloo}{Waterloo, ON}
\lineSummary{Implementing C++ and Python nodes on ROS-run Turtlebot for navigation research.}
% \lineSummary{Setting up and operating ROS-run Turtlebot for social navigation research purposes.}
% \listBegin
% \listItem{Wrote C++ and Python nodes to implement navigation stack on Turtlebot.}
% \listItem{Published sensor, odometry and transform messages to mobile base.}
% \listItem{Adapted existing open-source code for advanced algorithms: person-detection, SLAM navigation.}
% \listItem{Gained immense troubleshooting experience associated with accommodating open-source software.}
% \listEnd
